{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
added properties of the next function
added intuition of the first three rules

An important hypothesis to succeed in the proof of this theorem is the existence
of a \texttt{next} function. This \texttt{next} function should compute for every
high program point the first subsequent program point with a low security level. With
this function one is able to detect when a hidden thread is allowed to become visible
again.
\subsection{Instantiation}
\label{sec:instantiation}

>>>>

An important hypothesis to succeed in the proof of this theorem is the existence
of a \texttt{next} function. This \texttt{next} function should compute for every
high program point the first subsequent program point with a low security level. With
this function one is able to detect when a hidden thread is allowed to become visible
again.

This intuition is capture in the following properties for the function $next: \mathcal{P}
\rightharpoonup \mathcal{P}$:

\begin{enumerate}
\item $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}

Die domain of next just captures the high, but not always high program points (i.e. the ones
that can result in a hidden thread). The second property, states that two directly successive high
program points have the same program point in which the thread becomes visible again. The third rule
is the counterpart of the second: If a low program point follows a high program point, this low program
point is the result of the next function for the high program point.

\subsection{Instantiation}
\label{sec:instantiation}
